%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
        {AI Face Couting Application}{github link}
        {Technologies/Python}
        {This is a research project for the course Computer Vision at the University of North Carolina in Charlotte. The goal of this project is to implement student counting using an image. The model that was used is YOLOv6 and the dataset used is the COCO dataset. The model was trained on Google Colab and the results were tested on a local machine. The model was trained on 100 epochs and the results were tested on 100 images. The results were not as expected and the model was not able to detect students in the images. The model was able to detect people in the images but not students}

    \resumeProjectHeading
        {Online Store}{github link}
        {Technologies/Django}
        {This repository contains template code for a simple online store, built for my students in ITSC 3155 - Software Engineering at UNC Charlotte. Since the code is written as a starting template for students' group final projects, this repository should not be seen as a complete, production-ready online store. Functional features like user session management, database access, unit testing, and server-side rendering are included but kept at an abstract level. Users are instructed to fork this repository and customize it to the needs of their own project}

    \resumeProjectHeading
        {Burger Maker Abstraction}{github link}
        {Technologies/Java}
        {A console Application aimed to assist student to understanding the basic abstraction and polymorphiasm of Java}


\resumeSubHeadingListEnd
