\newParagraph{
Dear Hiring Manager,
}

\newParagraph{
With great sincerity, I would like to express my interest in a Theory Engineer position at \companyName.
I am currently a Master's student at the University of North Carolina at Charlotte, and while I will not be graduating until December, all that remains is the completion of my thesis.
As a result, I am looking for full-time employment at a company whose goals align with my research interests.
}

\newParagraph{
Although I have contributed to various projects in continual reinforcement learning, EEG signal processing, and projection pursuit, my primary research focus is on utilizing low-rank approximation methods for second-order optimization in real-world machine learning problem settings.
To put it succinctly, my work aims to reduce the computational complexity of second-order optimization and investigates how and why different types of data affect the performance of these methods.
}

\newParagraph{
While researching and pursuing my degree, I have also worked as an Instructional Assistant for graduate courses in Software Engineering and Programming Languages.
I used these positions as an opportunity to develop functional software by creating an automatic grading system for both courses.
In this process, I gained valuable experience in writing test-driven, clean code that is easy to maintain and extend.
The tools I created for these courses are being used as a model for future courses, and I am happy to see that my work will make the lives of future students and instructors easier. 
}

\newParagraph{
I am confident that my skills and enthusiasm would make me a valuable addition at \companyName.
And though I am still enrolled in school, I am willing to make any necessary arrangements to ensure this position would be my top priority.
Thank you for considering my application. I look forward to any feedback you may have.
}

\newParagraph{
Sincerely,\\
\myName
}